Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-07-17 tex/Main Text/manuscript.tex
写完引言第二段

\section*{Results}
%tag 结果1: 指数划分结构
\subsection*{Water utilization regimes}
% 这一节主要展示BCDI的变化趋势和WUR的划分
By the two significantly detected change points,
the changes of IWRU index are split into three periods, 
whose slopes are various and mainly contributed by different factors (Figure~\ref{fig:IWRU}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
and the lightening of water stresses made the most striking contribution (124\%), 
while tendentiousness and pattern of the water utilization had slight negative contribution.
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, 
despite positive contributions of tendentiousness and pattern of water utilization,
because of increasing stresses on water resource playing a larger negative role (-146\%). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization tendentiousness and pattern, 
and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总的来说，用水三个维度的组合呈现出阶段特征明显，但缓慢过渡的变化趋势
Taken together, combining the three dimensions of water resources utilization, 
whose regimes have clear phase-characteristics with gradual transitions between different phases (Figure~\ref{fig:phases}).

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/phases.pdf}
	\caption{Combination of three dimensions of water utilization regimes in three different periods. 
	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.}
	\label{fig:phases}
\end{figure}

%tag 结果2
\subsection*{Changes between different regimes}

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:changes}
\end{figure}

\subsection*{Main drivers of the regime shifts}

\subsection*{Language-Editing Services}
Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at www.pnas.org/page/authors/language-editing). PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.

\subsection*{Digital Figures}

EPS, high-resolution PDF, and PowerPoint are preferred formats for figures that will be used in the main manuscript. Authors may submit PRC or U3D files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format. Colour images must be in RGB (red, green, blue) mode. Include the font files for any text.

Images must be provided at final size, preferably 1 column width (8.7 cm). Figures wider than 1 column should be sized to 11.4 cm or 17.8 cm wide. Numbers, letters, and symbols should be no smaller than 6 points (2 mm) and no larger than 12 points (6 mm) after reduction and must be consistent.

Figures and tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.

\subsection*{Tables}
Tables should be included in the main manuscript file and should not be uploaded separately.

\begin{table}%[htbp]
	\centering
	\caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
	\begin{tabular}{lrrr}
		Species & CBS & CV & G3 \\
		\midrule
		1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
		2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
		3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
		\bottomrule
	\end{tabular}

	\addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
\end{table}

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:framework}
\end{figure}

>>>>

\section*{Results}
%tag 结果1: 指数划分结构
\subsection*{Water utilization regimes}
% 这一节主要展示BCDI的变化趋势和WUR的划分
By the two significantly detected change points,
the changes of IWRU index are split into three periods, 
whose slopes are various and mainly contributed by different factors (Figure~\ref{fig:IWRU}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/index.pdf}
	\caption{Changes of the IWRU index. 
	\textbf{A,} with two change points in 1978 and 1994, three periods were detected in trend of the IWRU.
	\textbf{B,} changes of IWRU in three periods have various slopes, while the second period have a negative growths rate.
	\textbf{C,} changes of the IWRU within three certain periods, which have different main contributors.
	}
	\label{fig:IWRU}
\end{figure}
% 接下来分句介绍每个阶段的特征
% 第一阶段
In the first period (P1, 1965-1978), the IWRU index had a rapidly increasing 
and the lightening of water stresses made the most striking contribution (124\%), 
while tendentiousness and pattern of the water utilization had slight negative contribution.
% 第二阶段
In the second period (P2, 1979-1994), the IWRU index experienced a slight drop, 
despite positive contributions of tendentiousness and pattern of water utilization,
because of increasing stresses on water resource playing a larger negative role (-146\%). 
% 第三阶段
However, as the further increasing of positive contributions of water utilization tendentiousness and pattern, 
and decelerations of water stresses in the third period (P3, 1995-2013), a positive growth of the IWRU returned.
% 总而言之，每个阶段都由水资源利用的不同维度提供最大的正向作用
As a result, each period is various in the most striking positive contributors to IWRU, 
corresponding to different dimensions of water utilization.

% 用水三个维度的组合呈现出阶段特征明显
Combining the three dimensions of water resources utilization, further more, 
sub-index regard to different water utilization dimensions were aggregative distinguishably in each same period, 
whose regimes show clear phase-characteristics (Figure~\ref{fig:phases}).
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/phases.pdf}
	\caption{Combination of three dimensions (S: stresses; T: tendentiousness; P: pattern) in different periods. 
	Size of the points denoting values of the IWRU: the mean of the P1 phase is 0.10, while 0.14, 0.19 in P2 and P3.
	The red indicator line in this ternary plot denotes 1:1 contributions between tendentiousness (T) and patterns (P).
	Two key change points (1978, 1994), along with the beginning (1965) and the ending (2013) of research period, are labelled.}
	\label{fig:phases}
\end{figure}
% 第一阶段到第二阶段
At the very beginning of research period (1965), high water stress domain the regime, 
while it experienced a large shift after entering P2 since 1978, 
with a change in the proportion of contributions between tendentiousness and pattern, too.
% 第三阶段集中
In contrast, the three dimensions' contribution were similar from 1994 into P3 to 2013, 
making the points highly concentrated at the centre of the ternary diagram for that period.
% 总之，出现制度
Taken all together, the three phases delineate distinct water resource utilization regimes, 
corresponding each period of.

%tag 结果2
\subsection*{Changes between different regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
A comparison of the phases under different dimensions reveals notable differences between each water use regime 
(Figure~\ref{fig:dimensions}).
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regime.
		\textbf{A,} changes of scarcity-flexibility-variability water stresses index (SFV-index).
		\textbf{B,} changes of non-provisioning water share, indicating water utilization tendentiousness.
		\textbf{C,} changes of water utilization pattern index.
		}
		\label{fig:dimensions}
	\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water stresses (Figure~\ref{fig:dimensions}A).
% 由于水资源压力由稀缺性、灵活性和变异性共同决定，P1-P2的变化主要看SFV
The P1, when water resources were the most abundant period, also had the least water consumption, 
while most of which were flexible water utilization.
Despite the rapid rise in water use during that period, numerous reservoirs were also built during this period, 
which increased storage capacities in each water-demand region to relief water resource stresses (SI).
However, entering P2, although water consumptions continued to increase, 
the number of new reservoirs was significantly reduced and the total storage capacity of each region was hardly increasing any more. 
Coupled with declining natural water resources, the water stress index of the basin was rapidly increasing.
% 另一方面，P2-P3，持续变化的水资源利用倾向与格局
On the other hand, as the most positive contributors to the IWRU index in P2 and P3, separately, 
tendentiousness and patterns of water utilization were still enlarging their impacts (Figure~\ref{fig:dimensions}B and C). 
% 首先是用水比例的变化
Representing tendentiousness of water utilization, 
increasing non-provisioning share of water utilization were mainly contributed by larger industrial water consumptions and minor total water uses, 
while the influence of both is waning.
% 再讨论用水格局的变化
However, patterns of water utilization, with accelerating changes and larger contributions to the IWRU, 
were mainly benefited from the convergence of development paces between regions and the basin-wide intersectoral water balance.
% 最后，每个阶段起
In summary, the changes in various aspects of the water use characteristics of the Yellow River Basin over the past 60 years 
are reflected in the changes in the corresponding indicators of the three dimensions.

\subsection*{Drivers of regime shifts}
Two regime shifts had distinct main drivers.
% 第一个 regime shift 包含着

@@

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main_text/framework}
	\caption{Placeholder image of a frog with a long example legend to show justification setting.}
	\label{fig:framework}
\end{figure*}
